---
title: "Final project - text analytics on airbnb dataset"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE,
                      message = FALSE, 
                      cache = TRUE)
```

Text analytics on airbnb dataset mainly focused on the three areas: listings summary, amenities description and review comments. The frist part is the description of preprocessing, following by the overview section including analysis of data quality and the interesting questions to address in each area. 

## Preprocessing
Most of the preprocessing in text analytics was done in python. The python codes can be found in the jupyter notebook **TextAnalytics_preprocessing.ipynb** (https://github.com/chding12/EDAV_Final_Project/blob/master/TextAnalytics_preprocessing_NLP.ipynb). Originally we have **listingsAll.csv** and reviewsAll.csv containing airbnb dataset in the past 10 years. After the inital cleaning process (refer to https://github.com/chding12/EDAV_Final_Project/blob/master/clean_data.Rmd) based on listingsAll.csv, we created cleaned_data.csv containing the required columns.

In TextAnalytics_preprocessing.ipynb, 4 steps are executed to complete the preprocessing for text analytics. The dataset was first loaded into pandas dataframe (https://pandas.pydata.org/) and then processed. 

1. Add rating ategory to the cleaned file
We created a new column by assigning each listing with a category based their review scores. The distribution of review scores is shown in 1.3 ratings distribution of the Overview section and is used as references to create 3 categories of ratings (A, B and C). The new column "rating_categ" was combined to the cleaned data to create **CleanedPlus.csv**. 

2. Adjective words in summary for visualization
In order to plot a wordcloud of adjective words in summary, we created a table of words and its frequencies for each rating category. We first tokenized summary text in each rating category into individual words and did pos tagging to identify the part-of-speech tag of each word. As pos-tagging is case-sensitive, we only turned each words into lowercases later. The finalized data  with three columns (word, freq, category) was written to **adj_summary.csv**, consisting of all the three rating categories. This dataset is later used in the 2.1 and 2.2 of the Summary section.

3. Adjective words in review for visualization
We worked on review comments from reviewsAll.csv. (1) The review comments was tokenized into individual words. (2) English stopwords, such as "a", "the", etc..., were removed from the words. (3) Post tagging. (4) Find adjective words. (5) Find nouns. (6) Count the number of adjective, noun and total words. After the preprocessing, we kept only required columns for visualization to **reviewsPlus.csv**. This dataset is used in 1.1 for data quality analysis and in 4.2 to 4.4 of the Review section. Moreover, we counted adjective words in each rating category and stored the data of three columns (word, freq, category) to **adj_reviews.csv** for wordcloud visualization in 4.1 of the Review section. 

4. Amenities word frequency
Key words of amenities description were extracted and counted. The words and frequencies of amenities were written to **amenities.csv** for 3.1 in the Amenities section. 

## I. Overview
```{r}
listingsAll <- read.csv('listingsAll.csv', stringsAsFactors=FALSE, sep=",", na.strings=c("","NA"))
cleanedPlus <- read.csv("CleanedPlus.csv", stringsAsFactors=FALSE, sep=",")
reviewsPlus <- read.csv('reviewsPlus.csv', stringsAsFactors=FALSE, sep=",")
```
We first loaded the listings, cleaned file with rating category and reviews datasets. 

### 1.1 Analysis of data quality - review data
```{r fig.width=5, fig.height=5}
library(extracat)
visna(reviewsPlus, sort='c')

na_ind <- which(is.na(reviewsPlus$comments) == TRUE)
length(na_ind)
nrow(reviewsPlus)
length(na_ind)/nrow(reviewsPlus)
```
Here we investigated the missing data pattern in the review dataset. As you can see from the above figure, only one missing data pattern is observed. In the column of comments, some data is missing. It is hard to see the very thin red color representing the number of missing rows (870) in the plot, as he percentage of missing rows are very few (less than 0.001%) given the total number of rows is 896208. As you might observe that while comments are null, the newly created columns from the text preprocessing (number of words, adj and noun) are not null. Even they are supposed to be null due to lack of comments, other values instead of NA were used in the preprocessing. Later to analyze review comments in section IV, all the rows where comments are null were removed.   
 
### 1.2 Analysis of data quality - listing data of summary and review scores only
```{r}
ls <- listingsAll %>%
  select(summary, review_scores_rating)
visna(ls, sort='c')
```

As you can see from the above plot, three missing pattern of summary and review scores in the listingsAll dataset are present. Most listings have both reviews scores and summary. Records having missing value in review scores only are around 1/3 of the complete recoreds, while a very small portion of records miss only summary or both reviews scores and summary. As we needed both summary and review scores for later text analysis, rows where either of these two columns are null were removed before ploting the reviews scores distribution in 1.3.  

### 1.3 ratings distribution
```{r}
library(dplyr)
mydata1 <- ls %>%
  dplyr::filter(!is.na(review_scores_rating))

hist(mydata1$review_scores_rating)
```

The purpose of this plot is to observ the distribution of review scores of each listing to come up with three rating categories. Category A indicates excellent listings with reviews scores from 90 to 100. Category B represent the good listings with reviews scores ranging between 75 to 90. Category C is a group of not-so-good listings where reviews scores are less than 75. It is interesting to notice that the majority of listings have high review scores. 

## II. Listing summary
### 2.1 which adjective words appear most frequently in listing summary?

```{r}
#install.packages("wordcloud") 
#install.packages("RColorBrewer") 
library(wordcloud)
library(RColorBrewer)

adj_s_all <- read.csv('adj_summary.csv', stringsAsFactors=FALSE,sep = "#")
adj_s_all$freq <- as.numeric(adj_s_all$freq)
```

We loaded preprocessed summary dataset from adj_summary.csv. All the three rating category are in this data and it contains word frequency of each rating category.  
```{r fig.height=8, fig.width=8}
#all
words_to_remove <- c('nan', 'll')

s1 <- adj_s_all %>%
  select(c("word", "freq")) %>%
  group_by(word) %>%
  summarize(freq=sum(freq)) %>%
  filter(!word %in% words_to_remove)

wordcloud(words = s1$word, freq = s1$freq,
                      min.freq = 1,
          max.words=200, random.order=FALSE, rot.per=0.35,
          colors=brewer.pal(8, "Paired"))
```

As we can see from the wordcloud representing most common adjective words in the listing summary, "private" is the most frequently used words to describe a listing. The other common words can be divided into two groups. First group, such "beautiful", "great", "comfortable", expresses abstract ideas of the venue to stimulate reader's imagination, while the second group, such as "new", "quiet", "spacious", "large", "clean", gives readers more hints on the physical condition of the place to bring vivid pictures in user's imagination. 

### 2.2 Are words of summary in each rating category the same?
```{r fig.height=8, fig.width=8}
library(ggplot2)

adj_s_all %>%
  group_by(category) %>%
  top_n(n=10, wt=freq) %>%
  ungroup() %>%
  ggplot(aes(reorder(word, freq), freq, fill = category)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~category, scales = 'free') +
  labs(y = "words frequency",
       X="most frequent words") +
  coord_flip()
```

Top 10 common adjective words are very similar among the three rating categories. Each group has one or two word different from the other group. Group A has the word "new", which does not appear in group B or C. Group A and Group B both has the word "comfortable", which is not present in group C. Both group B and C has the word "good", which is not in the top list in group A. In group C, without "new" and "comfortable", it has "available" instead. In conclusion, group A has "new" and "comfortable", while group B has "comfortable" and "good", and group C has "good" and "available". It is interesting to see that subtle change of word usage in the summary of listings from each rating group, isn't it?     

## III. Amenities
### 3.1 What are the most frequent amenities words?
```{r fig.height=8, fig.width=8}
amenities <- read.csv("amenities.csv", stringsAsFactors=FALSE,sep = "#")

amenities <- amenities[!startsWith(amenities$word, "translation missing"),]

wordcloud(words = amenities$word, freq = amenities$freq, min.freq = 1,
          max.words = 200, random.order=FALSE, rot.per=0.35,
          colors=brewer.pal(8, "Dark2"))

```

Word frequency of amenities in listings are shown in the above wordcloud figure. When it comes to amenities, listing owners are mostly concerned with three areas basics, technology and safety. 

- Basics: "essentials", "hangers", "shampoo", "hair dryer"
- General Facility: "kitchen", "heating", "air conditioning"
- Technology: 'Wifi", "laptop friendly workspace", "internet"
- Safety: "smoke detector", "carbon monoxide detector", "fire extinguisher".

Apparently, "kitchen", "heating" and "air conditioning", which provides comfort to a venue, are very often mentioned as part of the amenities provided by the listing. Safety is considered very important by the owners as those three words are comparably large as well. In terms of technology, "Wifi", providing our connection to the world, is as essential as elements providing pyhsical comfort such as "kitchen"" or "heating". Commonly mentioned items in basics include "hangers", "hair dryer" and "shampoo". These things are comparably easier to provide and it is nice to have them when visitors temporily stay at a place.

## IV. Reviews
### 4.1 Which words appear in high-rating or low-rating reviews?
```{r fig.width=8, fig.height=8}
library(tidytext)
library(reshape2)

adj_r <- read.csv("adj_review.csv", stringsAsFactors=FALSE,sep = "#")
adj_r_A <- adj_r %>%
  filter(category == 'A') %>%
  top_n(n=200, wt=freq)

adj_r_C <- adj_r %>%
  filter(category == 'C') %>%
  top_n(n=200, wt=freq)

# words in high-rating reviews
df_A <- adj_r_A %>%
  inner_join(get_sentiments("bing")) 
wordcloud(df_A$word, df_A$freq,
          ordered.colors=TRUE, max.words = 200, 
          colors=brewer.pal(8, "Dark2")[factor(df_A$sentiment)])

# words in low-rating reviews
df_C <- adj_r_C %>%
  inner_join(get_sentiments("bing")) 
wordcloud(df_C$word, df_C$freq,
          ordered.colors=TRUE, max.words = 200, 
          colors=brewer.pal(8, "Dark2")[factor(df_C$sentiment)])

```

We first did sentiment analysis on the adjective words of the reivews to identify words with positive or negative sentiments. As it is shown in the above two wordclouds, mostly positive words appeared in the reviews of listings with good ratings (Group A). As we moved to group C, although we could still see a few positive words in the reviews, more negative words appeared. Moreover, some words, such as "wonderful", "super", and "fantastic", to express exceptionally good feelings or opinions became less obvious or disappeared in the group C wordcloud.

### 4.2 Is the length of reviews of each room-type or borough different?
```{r}
rp <- reviewsPlus[complete.cases(reviewsPlus),]

col_to_select <- c("id", "room_type", "neighbourhood_group_cleansed", 'rating_categ')
sc <- cleanedPlus %>%
  select(col_to_select)

gl <- rp %>%
  group_by(listing_id) %>%
  summarize(
    mean_adj=as.integer(mean(number_adj)),
    total_adj=sum(number_adj),
    mean_noun=as.integer(mean(number_noun)),
    total_noun=sum(number_noun),
    mean_words=as.integer(mean(number_words)),
    total_words=sum(number_words),
    review_counts=n(),
    perc_adj=total_adj/total_words,
    perc_noun=total_noun/total_words,
    perc_other=1-(perc_adj+perc_noun)
  ) %>%
  inner_join(sc, by = c("listing_id" = "id"))


```

```{r}
# library(vcd)
r1 <- gl %>%
  group_by(neighbourhood_group_cleansed, room_type) %>%
  dplyr::summarise(avg_words = mean(mean_words))

# Use position=position_dodge()
p <- ggplot(data=r1, aes(x=neighbourhood_group_cleansed, 
                    y=avg_words, fill=room_type)) +
geom_bar(stat="identity", position=position_dodge())

p + scale_fill_brewer(palette="Dark2")

```



### 4.3 Is the length of review on each type of rooms different? 
```{r fig.width=5, fig.height=5}
library(grid)
r2 <- gl %>%
  group_by(rating_categ, room_type) %>%
  dplyr::summarise(avg_words = mean(mean_words))

# mosaic plot  
r2$room_type <- as.factor(r2$room_type)
r2$rating_categ <- as.factor(r2$rating_categ)

r2t <- xtabs(avg_words ~ rating_categ+room_type,
                   r2)
m2 <- vcd::mosaic(rating_categ~room_type, data=r2t,
                  gp = gpar(fill = colors()[1:3]))

# bar chart
p <- ggplot(data=r2, aes(x=rating_categ, 
                    y=avg_words, fill=room_type)) +
geom_bar(stat="identity", position=position_dodge())
p + scale_fill_brewer(palette="Spectral")
```

### 4.4 Does the length of reviews become shorter or longer over time?
```{r fig.width=5, fig.height=5}
rpg <- rp %>%
  left_join(sc, by = c("listing_id" = "id"))

rpg$date <- as.Date(rpg$date)
rpg$month <- as.Date(cut(rpg$date, breaks = "month"))
rpg$week <- as.Date(cut(rpg$date, breaks = "week"))
```

#### monthly changes over years
```{r}
r3 <- rpg %>%
  filter(date > "2014-01-01" & date <"2018-04-01") %>%
  group_by(month, room_type) %>%
  dplyr::summarise(avg_words = mean(number_words))

p <- ggplot(r3, aes(x=month, y=avg_words)) +
  geom_line(aes(color=room_type), size=1)

p + scale_colour_brewer(palette = "Set1")
```

#### weekly changes in 2017
```{r}
r3 <- rpg %>%
  filter(date > "2017-01-01" & date <"2018-01-31") %>%
  group_by(week, room_type) %>%
  dplyr::summarise(avg_words = mean(number_words))

p <- ggplot(r3, aes(x=week, y=avg_words)) +
  geom_line(aes(color=room_type), size=1) 

p + scale_colour_brewer(palette = "Set1")

```
